%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {R\&D Intern} % Job title
    {Sandia National Laboratories} % Organization
    {Livermore, CA} % Location
    {Jun. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Helped modernize a threat analytic and intrusion detection tool by supporting cloud computing traffic.}
        \item{Developed a smooth workflow between Cloud Service Providers to enable log aggregation and analysis.}
        \item{Rewrote dated frontend for a malware repository and multi-tool runner using React for better presentation and accessibility.}
        \item{Participated in discussions on Adversarial Machine Learning and privacy-preserving methods such as Differential Privacy, Homomorphic Encryption, and Secure Multi-party Computation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Center for Information and Computation Security (CICS), UCLA} % Organization
    {Los Angeles, CA} % Location
    {December 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Implemented an efficient and secure method to perform k-means clustering with provable security.}
        \begin{itemize}
          \item{Enables two parties to compute on their joint data while hiding their actual data from each other.}
          \item{Will submit to IEEE S\&P 2022.}
        \end{itemize}
        \item{Develop a reputation system for peer-to-peer networks with an emphasis on Blockchain with robust fairness and security (against malicious users) guarantees.}
        \begin{itemize}
          \item{Novel approach using Markov chains and Google's PageRank algorithm.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Independent Research (Prof. Rafail Ostrovsky)} % Organization
    {Los Angeles, CA} % Location
    {September 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed and implemented a novel linear-time secure merge algorithm.}
        \item{Only requires black-box access to a Group Homomorphic Encryption scheme.}
        \item{Asymptotically optimal and beats existing secure-merge protocols in both time and space.}
        \item{Introduces clever shuffle algorithm to efficiently create a linked list to obliviously traverse permuted lists.}
        \item{Introduces generalizable technique to convert ciphertexts into secret shares without computing an expensive decryption circuit jointly under MPC.}
        \item{To appear in CSCML 2022.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Stealth Software Technologies Inc.} % Organization
    {Los Angeles, CA} % Location
    {Sept. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Deployed multiple instances of an application on AWS instances with network configured using real-time constructed expander
graph.}
        \item{Used RabbitMQ to efficiently send and queue messages between instances.}
        \item{Implemented a custom flooding algorithm to reduce redundancy in network traffic.} 
        \item{Automated the entire task with robust error handling.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cventry
{Research Intern} % Job title
{Stealth Software Technologies Inc.} % Organization
{Los Angeles, CA} % Location
{Jun. - Sept. 2019, Jun. - Aug. 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Learned cryptography frameworks and languages.}
    \item{Analyzed and implemented algorithms for Secure Multi-party Computation for statistics such as Linear Regression and Crosstabs.}
    \item{Benchmarked existing secure frameworks to analyze factors such as communication cost and time taken.}
    \item{Surveyed existing literature on secure compaction and merge and compared actual running time.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
