%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

\cventry
{Officer, Content Lead} % Job title
{ACM ICPC at UCLA} % Organization
{Los Angeles, CA} % Location
{Oct. 2019 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Create and teach workshops for Competitive Programming and Technical Interview preparation.}
    \item{Taught nearly 25-30 regular
students Competitive Programming at a beginner-level weekly last Spring.}
    \item{Actively deliberate on how to make competitive programming more accessible to UCLA students. Introduce ideas to make content more approachable for students with no prior experience.}
    \item{Content Lead for Bruin Quest, a puzzle hunt and one of the biggest collaborations between three clubs under ACM.}
  \end{cvitems}
}

%---------------------------------------------------------

\cventry
    {Co-Tech Director} % Job title
    {LA Hacks} % Organization
    {Los Angeles, CA} % Location
    {Oct. 2018 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Led a small team in various collaborative projects including teaching the various tools and frameworks used.}
        \item{Followed professional coding practice and version control (Git) to manage codebase.}
        \item{Used React and SCSS to implement frontend. Developed backend in Go.}
        \item{Used industry tools like Docker to containerize micro-
        services.}
        \item{Managed and maintained frameworks used by more than 3000 people every year.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mentor} % Job title
    {MentorSEAS} % Organization
    {Los Angeles, CA} % Location
    {Sept. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Mentored incoming freshmen and transfer students to familiarize them with the campus, UCLA Engineering and available resources.}
        \item{Organized events both virtually and in-person to foster a sense of community and friendship between students.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
