%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Creator \& Active Developer} % Role
    {Discord Verification Bot} % Event
    {ACM at UCLA} % Location
    {Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Built a robust Discord bot in less than 72 hours to verify members on ACM at UCLA’s Official Discord server using Node.js, SQLite and Amazon SES for email.}
        \item{Verifies users using their UCLA email address and support various commands such as lookup for moderation purposes.}
        \item{It currently handles more than 2000 members and features automatic restarting on crash and automatic backups using system cron jobs.}
        \item{Hosted on an AWS EC2 instance.}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Co-creator} % Role
    {easyBay — ML-powered Advanced Image Search for eBay} % Event
    {Hacktech 2019, Caltech} % Location
    {Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Built an iOS app using Google Cloud’s Vision API and eBay’s Finding and Browse APIs.}
        \item{User could query products based on an image and certain filters.}
        \item{The image would be further processed by Google’s Vision API to return cropped objects.}
        \item{Increased image searching power and accuracy manifold.}
        \item{Products were also filtered out based on suspicion analyzed by a trained ML model.}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Co-creator} % Role
    {Listen — Salient Speech-to-text for Meetings and Lecture} % Event
    {HackUCI 2019, UCI} % Location
    {Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Created a web app that implements the find functionality for audio files.}
        \item{Playback an audio file from any instance of a word you type.}
        \item{The app also summarizes the audio file by giving keywords (based on their importance to the context) that acted as an executive summary.}
        \item{Made using Jinja, Flask and Python with the Google Cloud Platform for speech-to-text, Natural Language Processing, and Cloud Storage.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
