%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\resumesection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \resumeentry
    {R\&D Intern} % Job title
    {Sandia National Laboratories} % Organization
    {Livermore, CA} % Location
    {Jun. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Modernized a threat and intrusion detection tool by supporting cloud computing traffic.}
        \item{Developed a smooth workflow between Cloud Service Providers to enable log aggregation and analysis.}
        \item{Participated in discussions on Adversarial Machine Learning and privacy-preserving methods such as Differential Privacy, Homomorphic Encryption, and Secure Multi-party Computation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \resumeentry
    {Undergraduate Researcher} % Job title
    {Center for Information and Computation Security (CICS), UCLA} % Organization
    {Los Angeles, CA} % Location
    {December 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed and implemented a novel linear-time secure merge algorithm using Homomorphic Encryption. Introduces clever shuffle algorithm to efficiently traverse permuted lists obliviously. (To appear in CSCML 2022.)}
        \item{Implemented an efficient and secure method to perform k-means clustering with provable security. Enables two parties to compute on their joint data while hiding their actual data from each other. Will submit to IEEE S\&P 2022.}
        \item{Develop a reputation system for peer-to-peer networks with an emphasis on Blockchain with robust fairness and security (against malicious users) guarantees. Novel approach using Markov chains and Google's PageRank algorithm.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \resumeentry
    {Software Engineer \& Research Intern} % Job title
    {Stealth Software Technologies Inc.} % Organization
    {Los Angeles, CA} % Location
    {Jun. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Analyzed and implemented algorithms for Secure Multi-party Computation for statistics such as Linear Regression and Crosstabs.}
        \item{Benchmarked existing cryptographic frameworks to analyze factors such as communication cost and time taken.}
        \item{Deployed multiple instances of an application on AWS instances with network configured using real-time constructed expander graph.}
        \item{Used RabbitMQ to efficiently send and queue messages between instances.}
        \item{Implemented a custom flooding algorithm to reduce redundancy in network traffic.} 
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
